---
title: "Cox Model - PTEN PanCancer (PFI)"
output:
  word_document: default
  html_notebook: default
  pdf_document: default
---

#Cox Model Cox Model results of Progression Free Interval (PFI) from 30 different tumor types. PTEN SCNA was used as design formula.

```{r include=FALSE}
library(ggplot2)
library(ggsignif)
library(ggpubr)
library(survminer)
library(survival)
library(ranger)
library(tidyverse)
library(ggfortify)
library(egg)
```

```{r include=FALSE}
teste <- read_tsv("clinical_PanCancer_PTEN_2.txt",
                  col_names = T)
teste$PTEN_SCNA_status <- factor(teste$PTEN_SCNA_status, levels = c("Intact","HomDel","HemDel"))
```

```{r include=FALSE}
acc <- teste %>% filter(TCGA_Study == c("ACC"))
blca <- teste %>% filter(TCGA_Study == "BLCA")
brca <- teste %>% filter(TCGA_Study == "BRCA")
brain <- teste %>% filter(TCGA_Study ==  c("GBM", "LGG"))
cesc <- teste %>% filter(TCGA_Study == "CESC")
coad <- teste %>% filter(TCGA_Study == "COAD")
dlbc <- teste %>% filter(TCGA_Study == "DLBC")
esca <- teste %>% filter(TCGA_Study == "ESCA")
hnsc <- teste %>% filter(TCGA_Study == "HNSC")
kich <- teste %>% filter(TCGA_Study == "KICH")
kirc <- teste %>% filter(TCGA_Study == "KIRC")
kirp <- teste %>% filter(TCGA_Study == "KIRP")
lihc <- teste %>% filter(TCGA_Study == "LIHC")
luad <- teste %>% filter(TCGA_Study == "LUAD")
lusc <- teste %>% filter(TCGA_Study == "LUSC")
meso <- teste %>% filter(TCGA_Study == "MESO")
ov <- teste %>% filter(TCGA_Study == "OV")
paad <- teste %>% filter(TCGA_Study == "PAAD")
pcpg <- teste %>% filter(TCGA_Study == "PCPG")
prad <- teste %>% filter(TCGA_Study == "PRAD")
read <- teste %>% filter(TCGA_Study == "READ")
sarc <- teste %>% filter(TCGA_Study == "SARC")
skcm <- teste %>% filter(TCGA_Study == "SKCM")
stad <- teste %>% filter(TCGA_Study == "STAD")
tgct <- teste %>% filter(TCGA_Study == "TGCT")
thca <- teste %>% filter(TCGA_Study == "THCA")
thym <- teste %>% filter(TCGA_Study == "THYM")
ucec <- teste %>% filter(TCGA_Study == "UCEC")
ucs <- teste %>% filter(TCGA_Study == "UCS")
uvm <- teste %>% filter(TCGA_Study == "UVM")
```

```{r include=FALSE}
acc_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = acc)
acc_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=acc)

blca_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = blca)
blca_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=blca)

brca_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = brca)
brca_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=brca)

brain_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = brain)
brain_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=brain)

cesc_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = cesc)
cesc_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=cesc)

coad_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = coad)
coad_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=coad)

dlbc_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = dlbc)
dlbc_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=dlbc)

esca_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = esca)
esca_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=esca)

hnsc_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = hnsc)
hnsc_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=hnsc)

kich_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = kich)
kich_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=kich)

kirc_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = kirc)
kirc_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=kirc)

kirp_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = kirp)
kirp_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=kirp)

lihc_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = lihc)
lihc_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=lihc)

luad_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = luad)
luad_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=luad)

lusc_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = lusc)
lusc_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=lusc)

meso_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = meso)
meso_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=meso)

ov_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = ov)
ov_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=ov)

paad_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = paad)
paad_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=paad)

pcpg_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = pcpg)
pcpg_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=pcpg)

prad_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = prad)
prad_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=prad)

read_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = read)
read_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=read)

sarc_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = sarc)
sarc_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=sarc)

#skcm_cox <- coxph(Surv(OS_Time, OS) ~ PTEN_SCNA_status, 
#             data = skcm)

stad_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = stad)
stad_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=stad)

tgct_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = tgct)
tgct_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=tgct)

thca_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = thca)
thca_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=thca)

thym_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = thym)
thym_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=thym)

ucec_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = ucec)
ucec_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=ucec)

ucs_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = ucs)
ucs_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=ucs)

uvm_cox <- coxph(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, 
             data = uvm)
uvm_KM <- survfit(Surv(PFI_Time, PFI) ~ PTEN_SCNA_status, data=uvm)

```

**ACC**
Adrenocortical Carcinoma
```{r}
acc_plot <- ggsurvplot(acc_KM, pval = TRUE, risk.table = TRUE, 
                      title = "ACC", xlab="Time (Days)",
                      legend.labs = c("Intact", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
acc_plot
summary(acc_cox)

```

**BLCA**
Bladder Urothelial Carcinoma
```{r}
blca_plot <- ggsurvplot(blca_KM, pval = TRUE, risk.table = TRUE, 
                      title = "BLCA", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
blca_plot
summary(blca_cox)
```

**BRCA**
Breast Invasive Carcinoma
```{r}
brca_plot <- ggsurvplot(brca_KM, pval = TRUE, risk.table = TRUE, 
                      title = "BRCA", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
brca_plot
summary(brca_cox)
```

**BRAIN**
LGG, Brain Lower Grade Glioma, and GBM, Glioblastoma 
```{r}
brain_plot <- ggsurvplot(brain_KM, pval = TRUE, risk.table = TRUE, 
                      title = "Brain", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
brain_plot
summary(brain_cox)
```

**CESC**
Cervical Squamous Cell Carcinoma
```{r}
cesc_plot <- ggsurvplot(cesc_KM, pval = TRUE, risk.table = TRUE, 
                      title = "CESC", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
cesc_plot
summary(cesc_cox)
```

**COAD**
Colon Adenocarcinoma
```{r}
coad_plot <- ggsurvplot(coad_KM, pval = TRUE, risk.table = TRUE, 
                      title = "COAD", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
coad_plot
summary(coad_cox)
```

**DLBC**
Lymphoid Neoplasm Diffuse Large B-cell Lymphoma
```{r}
dlbc_plot <- ggsurvplot(dlbc_KM, pval = TRUE, risk.table = TRUE, 
                      title = "DLBC", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
dlbc_plot
summary(dlbc_cox)
```

**ESCA**
Esophageal Carcinoma
```{r}
esca_plot <- ggsurvplot(esca_KM, pval = TRUE, risk.table = TRUE, 
                      title = "ESCA", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
esca_plot
summary(esca_cox)
```

**HNSC**
Head and Neck Squamous Cell Carcinoma
```{r}
hnsc_plot <- ggsurvplot(hnsc_KM, pval = TRUE, risk.table = TRUE, 
                      title = "HNSC", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
hnsc_plot
summary(hnsc_cox)
```

**KICH**
Kidney Chromophobe Renal Cell Carcinoma
```{r}
kich_plot <- ggsurvplot(kich_KM, pval = TRUE, risk.table = TRUE, 
                      title = "KICH", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
kich_plot
summary(kich_cox)
```

**KIRC**
Kidney Renal Clear Cell Carcinoma
```{r}
kirc_plot <- ggsurvplot(kirc_KM, pval = TRUE, risk.table = TRUE, 
                      title = "KIRC", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
kirc_plot
summary(kirc_cox)
```

**KIRP**
Kidney Renal papillary Cell Carcinoma
```{r}
kirp_plot <- ggsurvplot(kirp_KM, pval = TRUE, risk.table = TRUE, 
                      title = "KIRP", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
kirp_plot
summary(kirp_cox)
```

**LIHC**
Liver Hepatocellular Carcinoma
```{r}
lihc_plot <- ggsurvplot(lihc_KM, pval = TRUE, risk.table = TRUE, 
                      title = "LIHC", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
lihc_plot
summary(lihc_cox)
```

**LUAD**
Lung Adenocarcinoma
```{r}
luad_plot <- ggsurvplot(luad_KM, pval = TRUE, risk.table = TRUE, 
                      title = "LUAD", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
luad_plot
summary(luad_cox)
```

**LUSC**
Lung Squamous Cell Carcinoma
```{r}
lusc_plot <- ggsurvplot(lusc_KM, pval = TRUE, risk.table = TRUE, 
                      title = "LUSC", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
lusc_plot
summary(lusc_cox)
```

**MESO**
Mesothelioma
```{r}
meso_plot <- ggsurvplot(meso_KM, pval = TRUE, risk.table = TRUE, 
                      title = "MESO", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
meso_plot
summary(meso_cox)
```

**OV**
Ovarian Serous Cystadenocarcinoma
```{r}
ov_plot <- ggsurvplot(ov_KM, pval = TRUE, risk.table = TRUE, 
                      title = "OV", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
ov_plot
summary(ov_cox)
```

**PAAD**
Pancreatic Adenocarcinoma
```{r}
paad_plot <- ggsurvplot(paad_KM, pval = TRUE, risk.table = TRUE, 
                      title = "PAAD", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
paad_plot
summary(paad_cox)
```

**PCPG**
Pheochromocytoma and Paraganglioma
```{r}
pcpg_plot <- ggsurvplot(pcpg_KM, pval = TRUE, risk.table = TRUE, 
                      title = "PCPG", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
pcpg_plot
summary(pcpg_cox)
```

**PRAD**
Prostate Adenocarcinoma
```{r}
prad_plot <- ggsurvplot(prad_KM, pval = TRUE, risk.table = TRUE, 
                      title = "PRAD", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
prad_plot
summary(prad_cox)
```

**READ**
Rectum Adenocarcinoma
```{r}
read_plot <- ggsurvplot(read_KM, pval = TRUE, risk.table = TRUE, 
                      title = "READ", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
read_plot
summary(read_cox)
```

**SARC**
Sarcoma
```{r}
sarc_plot <- ggsurvplot(sarc_KM, pval = TRUE, risk.table = TRUE, 
                      title = "SARC", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
sarc_plot
summary(sarc_cox)
```

**STAD**
Stomach Adenocarcinoma
```{r}
stad_plot <- ggsurvplot(stad_KM, pval = TRUE, risk.table = TRUE, 
                      title = "STAD", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
stad_plot
summary(stad_cox)
```


**TGCT**
Testicular Germ Cell Tumors
```{r}
tgct_plot <- ggsurvplot(tgct_KM, pval = TRUE, risk.table = TRUE, 
                      title = "TGCT", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
tgct_plot
summary(tgct_cox)
```


**THCA**
Thyroid Carcinoma
```{r echo=FALSE}
thca_plot <- ggsurvplot(thca_KM, pval = TRUE, risk.table = TRUE, 
                      title = "THCA", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
thca_plot
summary(thca_cox)
```

**THYM**
Thymoma
```{r echo=FALSE}
thym_plot <- ggsurvplot(thym_KM, pval = TRUE, risk.table = TRUE, 
                      title = "THYM", xlab="Time (Days)",
                      legend.labs = c("Intact", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
thym_plot
summary(thym_cox)
```


**UCEC**
Uterine Endometrioid Carcinoma
```{r echo=FALSE}
ucec_plot <- ggsurvplot(ucec_KM, pval = TRUE, risk.table = TRUE, 
                      title = "UCEC", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
ucec_plot
summary(ucec_cox)
```


**UCS**
Uterine Carcinosarcoma
```{r echo=FALSE}
ucs_plot <- ggsurvplot(ucs_KM, pval = TRUE, risk.table = TRUE, 
                      title = "UCS", xlab="Time (Days)",
                      legend.labs = c("Intact","HomDel", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","red2","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6,)
ucs_plot
summary(ucs_cox)
```


**UVM**
Uveal Melanoma
```{r echo=FALSE}
uvm_plot <- ggsurvplot(uvm_KM, pval = TRUE, risk.table = TRUE, 
                      title = "UVM", xlab="Time (Days)",
                      legend.labs = c("Intact", "HemDel"), legend.title = "",
                      pval.coord = c(0, 0.03), palette = c("forestgreen","dodgerblue2"),
                      legend = c(0.9, 0.9), ylab = "", 
                      ggtheme = theme_article(), pval.size = 6)
uvm_plot
summary(uvm_cox)
```
